Manuscript Figures for Genome Biology

### 2018-08-16 manuscript_figures/manuscript_figures.Rmd
Update filename parsing of yeast sb objs after expansion of simulations

# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|null|polyester"), dataset) &
            !grepl("scRNAseq", casestudy) &
            !grepl("uninf", dataset))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

>>>>

# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            grepl(c("yeast-"), dataset) &
            grepl("de", dataset) &
            !grepl("scRNAseq", casestudy) &
            !grepl("uninf", dataset))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))
